\begin{enumerate}

\item ``Realiz3D: 3D Generation Made Photorealistic via Domain-Aware Learning'', I.Sobol, K.Sohn, Y.Blum, E.Zakharov, M.Bluvstein, A.Vedaldi, \underline{O.Litany}, CVPR 2026.

\item ``InstructMix2Mix: Consistent Sparse-View Editing Through Multi-View Model Personalization'', D.Gilo, \underline{O.Litany}, CVPR 2026.

\item ``DiffusionHarmonizer: Bridging Neural Reconstruction and Photorealistic Simulation with Online Diffusion Enhancer'', Y.Zhang, K.Tothova, Z.Wang, K.Yin, H.Turki, Rd.Lutio, Y.Chang, \underline{O.Litany}, S.Fidler, Z.Gojcic, CVPR 2026.

\item ``Time-to-Move: Training-Free Motion-Controlled Video Generation via Dual-Clock Denoising'', A.Singer, N.Rotstein, A.Mann, R.Kimmel, \underline{O.Litany}, ICLR 2026.

\item ``SpaceControl: Introducing Test-Time Spatial Control to 3D Generative Modeling'', F.Engelmann, E.Fedele, I.Huang, \underline{O.Litany}, M.Pollefeys, L.Guibas, ICLR 2026.

\item ``Appreciate the View: A Task-Aware Evaluation Framework for Novel View Synthesis'', S.Stern, I.Sobol, \underline{O.Litany}, 3DV 2026.

\item ``Gaussian See, Gaussian Do: Semantic 3D Motion Transfer from Multiview Video'', Y.Bekor, G.Harari, O.Perel, \underline{O.Litany}, SIGGRAPH-ASIA 2025.

\item ``A Lesson in Splats: Teacher-Guided Diffusion for 3D Gaussian Splats Generation with 2D Supervision'', C.Peng, I.Sobol, M.Tomizuka, K.Keutzer, C.Xu, \underline{O.Litany}, ICCV 2025.

\item ``MonSTeR : a Unified Model for Motion, Scene, Text Retrieval'', L.Collorone, M.Gioia, M.Pappa, P.Leoni, G.Ficarra, \underline{O.Litany}, I.Spinelli, F.Galasso, ICCV 2025.

\item ``FRIDU: Functional Map Refinement with Guided Image Diffusion'', A.Cohen-Rimon, M.Ben-Chen, \underline{O.Litany}, SGP 2025.

\item ``OmniRe: Omni Urban Scene Reconstruction'', Z.Chen, J.Yang, J.Huang, Rd.Lutio, JM.Esturo, B.Ivanovic, \underline{O.Litany}, Z.Gojcic, S.Fidler, M.Pavone, L.Song, Y.Wang, ICLR 2025 \textcolor{red}{Spotlight}.

\item ``ReHub: Linear Complexity Graph Transformers with Adaptive Hub-Spoke Reassignment'', T.Borreda, D.Freedman, \underline{O.Litany}, TMLR.

\item ``Epi-NAF: Enhancing Neural Attenuation Fields for Limited-Angle CT with Epipolar Consistency Conditions'', D.Gilo, T.Klinghoffer, \underline{O.Litany}, ISBI 2025 \textcolor{red}{Oral}.

\item ``Robust Symmetry Detection via Riemannian Langevin Dynamics'', J.Je, J.Liu, G.Yang, B.Deng, S.Cai, G.Wetzstein, \underline{O.Litany}, L.Guibas, SIGGRAPH-ASIA 2024.

\item ``Zero-to-Hero: Enhancing Zero-Shot Novel View Synthesis via Attention Map Filtering'', I.Sobol, C.Xu, \underline{O.Litany}, NeurIPS 2024.

\item ``The NeRFect Match: Exploring NeRF Features for Visual Localization'', Q.Zhou, M.Maximov, \underline{O.Litany}, L.Leal-Taixé, ECCV 2024.

\item ``Dynamic LiDAR Re-simulation using Compositional Neural Fields'', H.Wu, X.Zuo, S.Leutenegger, \underline{O.Litany}, K.Schindler, S.Huang, CVPR 2024.

\item ``3DiffTection: 3D Object Detection with Geometry-Aware Diffusion Features'', C.Xu, H.Ling, S.Fidler, \underline{O.Litany}, CVPR 2024.

\item ``UnScene3D: Unsupervised 3D Instance Segmentation for Indoor Scenes'', D.Rozenberszki, \underline{O.Litany}, A.Dai, CVPR 2024.

\item ``Approximately Piecewise E(3) Equivariant Point Networks'', M.Atzmon, J.Huang, F.Williams, \underline{O.Litany}, ICLR 2024.

\item ``EmerNeRF: Emergent Spatial-Temporal Scene Decomposition via Self-Supervision'', J.Yang, B.Ivanovic, \underline{O.Litany}, X.Weng, SW.Kim, B.Li, T.Che, D.Xu, S.Fidler, M.Pavone, Y.Wang, ICLR 2024.

\item ``Multi-Track Timeline Control for Text-Driven 3D Human Motion Generation'', M.Petrovich, \underline{O.Litany}, U.Iqbal, MJ.Black, G.Varol, XB.Peng, D.Rempe, CVPR 2024 Workshop on Human Motion Generation.

\item ``Semi-Supervised Semantic Segmentation via Marginal Contextual Information'', M.Kimhi, S.Kimhi, E.Zheltonozhskii, \underline{O.Litany}, C.Baskin, TMLR.

\item ``Neural LiDAR Fields for Novel View Synthesis'', S.Huang, Z.Gojcic, Z.Wang, F.Williams, Y.Kasten, S.Fidler, K.Schindler, \underline{O.Litany}, ICCV 2023.

\item ``Towards Viewpoint Robustness in Bird’s Eye View Segmentation'', T.Klinghoffer, J.Philion, W.Chen, \underline{O.Litany}, Z.Gojcic, J.Joo, R.Raskar, S.Fidler, J.Alvarez, ICCV 2023.

\item ``Neural Kernel Surface Reconstruction'', J.Huang, Z.Gojcic, M.Atzmon, \underline{O.Litany}, S.Fidler, F.Williams, CVPR 2023 \textcolor{red}{Highlight (top 10\% of accepted papers)}.

\item ``Trace and Pace: Controllable Pedestrian Animation via Guided Trajectory Diffusion'', D.Rempe, Z.Luo, XB.Peng, Y.Yuan, KM.Kitani, K.Kreis, S.Fidler, \underline{O.Litany}, CVPR 2023.

\item ``Fast Monocular Scene Reconstruction with Global-Sparse Local-Dense Grids'', W.Dong, C.Choy, CT.Loop, Y.Zhu, \underline{O.Litany}, A.Anandkumar, CVPR 2023.

\item ``Mask3D for 3D Semantic Instance Segmentation'', J.Schult, F.Engelmann, A.Hermans, \underline{O.Litany}, S.Tang, B.Leibe, ICRA 2023.

\item ``GET3D: A Generative Model of High Quality 3D Textured Shapes Learned from Images'', J.Gao, T.Shen, Z.Wang, W.Chen, K.Yin, D.Li, \underline{O.Litany}, Z.Gojcic, S.Fidler, NeurIPS 2022.

\item ``LION: Latent Point Diffusion Models for 3D Shape Generation'', X.Zeng, A.Vahdat, F.Williams, Z.Gojcic, \underline{O.Litany}, S.Fidler, K.Kreis, NeurIPS 2022.

\item ``Language-Grounded Indoor 3D Semantic Segmentation in the Wild'', D.Rozenberszki, \underline{O.Litany}, A.Dai, ECCV 2022.

\item ``MVDECOR: Multi-view Dense Correspondence Learning for Fine-grained 3D Segmentation'', G.Sharma, K.Yin, S.Maji, E.Kalogerakis, \underline{O.Litany}, S.Fidler, ECCV 2022.

\item ``Learning Smooth Neural Functions via Lipschitz Regularization'', D.Liu, F.Williams, A.Jacobson, S.Fidler, \underline{O.Litany}, SIGGRAPH 2022.

\item ``Spectral Unions of Partial Deformable 3D Shapes'', L.Moschella, S.Melzi, L.Cosmo, F.Maggioli, \underline{O.Litany}, M.Ovsjanikov, L.Guibas, E.Rodolà, Eurographics 2022.

\item ``Generating Useful Accident-Prone Driving Scenarios via a Learned Traffic Prior'', D.Rempe, J.Philion, L.Guibas, S.Fidler, \underline{aO.Litany}, CVPR 2022.

\item ``Neural Fields as Learnable Kernels for 3D Reconstruction'', F.Williams*, Z.Gojcic*, S.Khamis, D.Zorin, J.Bruna, S.Fidler, \underline{O.Litany}, CVPR 2022.

\item ``Neural Fields in Visual Computing and Beyond'', Y.Xie, T.Takikawa, S.Saito, \underline{O.Litany}, S.Yan, N.Khan, F.Tombari, J.Tompkin, V.Sitzmann, S.Sridhar, Eurographics 2022 STAR.

\item ``DIB-R++: Learning to Predict Lighting and Material with a Hybrid Differentiable Renderer'', W.Chen, J.Litalien, J.Gao, Z.Wang, CF.Tsang, S.Khamis, \underline{O.Litany}, S.Fidler, NeurIPS 2021.

\item ``Mix3D: Out-of-Context Data Augmentation for 3D Scenes'', A.Nekrasov, J.Schult, \underline{O.Litany}, B.Leibe, F.Engelmann, 3DV 2021.

\item ``Vector Neurons: A General Framework for SO(3)-Equivariant Networks'', C.Deng, \underline{O.Litany}, Y.Duan, A.Poulenard, A.Tagliasacchi, L.Guibas, ICCV 2021.

\item ``Contrast to Divide: Self-Supervised Pre-Training for Learning with Noisy Labels'', E.Zheltonozhskii, C.Baskin, A.Mendelson, AM.Bronstein, \underline{O.Litany}, WACV 2022.

\item ``ReLMoGen: Integrating Reinforcement Learning and Motion Generation for Interactive Navigation'', F.Xia, C.Li, R.Martin-Martin, A.Toshev, \underline{O.Litany}, S.Savarese, ICRA 2021.

\item ``Weakly Supervised Learning of Rigid 3D Scene Flow'', Z.Gojcic, \underline{O.Litany}, A.Wieser, LJ.Guibas, T.Birdal, CVPR 2021.

\item ``Causal Scene Bert: Improving object detection by searching for challenging groups'', C.Resnick, \underline{O.Litany}, A.Kar, K.Kreis, J.Lucas, K.Cho, S.Fidler, ICCV workshop.

\item ``3DIoUMatch: Leveraging IoU Prediction for Semi-Supervised 3D Object Detection'', H.Wang*, Y.Cong*, \underline{O.Litany}, Y.Gao, LJ.Guibas, CVPR 2021.

\item ``Self-Supervised Equivariant Scene Synthesis from Video'', C.Resnick, \underline{O.Litany}, C.Heiß, H.Larochelle, J.Bruna, K.Cho, Neurips 2020 DiffCVGP workshop.

\item ``Representation Learning Through Latent Canonicalizations'', \underline{O.Litany}, A.Morcos, S.Sridhar, L.Guibas, J.Hoffman, WACV 2021.

\item ``Continuous Geodesic Convolutions for Learning on 3D Shapes'', Z.Yang, \underline{O.Litany}, T.Birdal, S.Sridhar, L.Guibas, WACV 2021.

\item ``PointContrast: Unsupervised Pretraining for 3D Point Cloud Understanding'', S.Xie, J.Gu, D.Guo, CR.Qi, L.Guibas, \underline{O.Litany}, ECCV 2020 \textcolor{red}{Spotlight}.

\item ``Towards Precise Completion of Deformable Shapes'', O.Halimi, I.Imanuel, \underline{O.Litany}, G.Trappolini, E.Rodolà, L.Guibas, R.Kimmel, ECCV 2020.

\item ``On Learning Sets of Symmetric Elements'', H.Maron, \underline{O.Litany}, G.Chechik, E.Fetaya, ICML 2020 \textcolor{red}{Outstanding Paper Award}.

\item ``ImVoteNet: Boosting 3D Object Detection in Point Clouds with Image Votes'', CR.Qi, X.Chen, \underline{O.Litany}, LJ.Guibas, CVPR 2020.

\item ``Deep Hough Voting for 3D Object Detection in Point Clouds'', CR.Qi, \underline{O.Litany}, K.He, LJ.Guibas, ICCV, 2019 \textcolor{red}{Best Paper Nomination}.

\item ``Dual-primal graph convolutional networks'', F.Monti, O.Shchur, A.Bojchevski, \underline{O.Litany}, S.Günnemann, MM.Bronstein, GEM workshop at ECML-PKDD, 2019 \textcolor{red}{Oral presentation}.

\item ``SOSELETO: A Unified Approach to Transfer Learning and Training with Noisy Labels'', \underline{O.Litany}, D.Freedman, ICLR workshop on Learning from Limited Labeled Data, 2019 \textcolor{red}{Best Paper Award}.

\item ``Self-supervised Learning of Dense Shape Correspondence'', O.Halimi, \underline{O.Litany}, E.Rodolà, A.Bronstein, R.Kimmel, Computer Vision and Pattern Recognition (CVPR), 2019 \textcolor{red}{Oral presentation}.

\item ``Deformable Shape Completion with Graph Convolutional Autoencoders'', \underline{O.Litany}, AM.Bronstein, MM.Bronstein, A.Makadia, Computer Vision and Pattern Recognition (CVPR), 2018.

\item ``Partial Single-and Multishape Dense Correspondence Using Functional Maps'', \underline{O.Litany}, E.Rodolà, A.Bronstein, M.Bronstein, D.Cremers, Handbook of Numerical Analysis, Elsevier, 2018.

\item ``Class-Aware Fully Convolutional Gaussian and Poisson Denoising'', T.Remez, \underline{O.Litany}, R.Giryes, AM.Bronstein, IEEE Transactions on Image Processing, 2018.

\item ``Efficient Deformable Shape Correspondence via Kernel Matching'', Z.Lähner, M.Vestner, A.Boyarski, \underline{O.Litany}, e.al., Intl. Conference on 3D Vision (3DV), 2017.

\item ``Deep Functional Maps: Structured Prediction for Dense Shape Correspondence'', \underline{O.Litany}, T.Remez, E.Rodolà, AM.Bronstein, MM.Bronstein, ICCV, 2017.

\item ``Deep Class Aware Image Denoising'', T.Remez, \underline{O.Litany}, R.Giryes, AM.Bronstein, IEEE International Conference on Image Processing (ICIP), 2017.

\item ``Cloud Dictionary: Sparse Coding and Modeling for Point Clouds'', \underline{O.Litany*}, T.Remez*, AM.Bronstein, Signal Processing with Adaptive Sparse Structured Representations (SPARS), 2017.

\item ``Fully Spectral Partial Shape Matching'', \underline{O.Litany}, E.Rodolà, AM.Bronstein, MM.Bronstein, Computer Graphics Forum, Vol. 36(2), 2017Presented at <em>Eurographics</em>, 2017.

\item ``SHREC`17: Deformable Shape Retrieval with Missing Parts'', E.Rodolà, L.Cosmo, \underline{O.Litany}, MM.Bronstein, AMBe.al., EUROGRAPHICS Workshop on 3D Object Retrieval (3DOR), 2017.

\item ``ASIST: Automatic Semantically Invariant Scene Transformation'', \underline{O.Litany}, T.Remez, D.Freedman, L.Shapira, A.Bronstein, R.Gal, Computer Vision and Image Understanding (CVIU), 2017.

\item ``Non-Rigid Puzzles'', \underline{O.Litany}, E.Rodolà, A.Bronstein, M.Bronstein, D.Cremers, Computer Graphics Forum, Wiley, volume 35, 2016 \textcolor{red}{SGP Best Paper Award}.

\item ``A picture is worth a billion bits: Real-time image reconstruction from dense binary threshold pixels'', T.Remez*, \underline{O.Litany*}, A.Bronstein, International Conference on Computational Photography (ICCP), 2016.

\item ``Image reconstruction from dense binary pixels'', \underline{O.Litany*}, T.Remez*, A.Bronstein, Signal Processing with Adaptive Sparse Structured Representations (SPARS), 2015.

\item ``Putting the pieces together: regularized multi-shape partial matching'', \underline{O.Litany}, A.Bronstein, M.Bronstein, Workshop on Nonrigid Shape Analysis and Deformable Image Alignment (NORDIA), 2012.

\end{enumerate}

\section{\sc Preprints}

\begin{enumerate}

\item ``Test-Time Training with KV Binding Is Secretly Linear Attention'', J.Liu, S.Elflein, \underline{O.Litany}, Z.Gojcic, R.Li, Preprint.

\item ``RadarGen: Automotive Radar Point Cloud Generation from Cameras'', T.Borreda, F.Ding, S.Fidler, S.Huang, \underline{O.Litany}, Preprint.

\item ``GAS-NeRF: Geometry-Aware Stylization of Dynamic Radiance Fields'', NPA.Vu, A.Saroha, \underline{O.Litany}, D.Cremers, Preprint.

\item ``ZDySS--Zero-Shot Dynamic Scene Stylization using Gaussian Splatting'', A.Saroha, F.Hofherr, M.Gladkova, C.Curreli, \underline{O.Litany}, D.Cremers, Preprint.

\item ``Federated Learning with Heterogeneous Architectures using Graph HyperNetworks'', \underline{O.Litany}, H.Maron, D.Acuna, J.Kautz, G.Chechik, S.Fidler, Preprint.

\item ``StrobeNet: Category-Level Multiview Reconstruction of Articulated Objects'', G.Zhang, \underline{O.Litany}, S.Sridhar, L.Guibas, Preprint.

\item ``Human 3D keypoints via spatial uncertainty modeling'', F.Williams, \underline{O.Litany}, A.Sud, K.Swersky, A.Tagliasacchi, Preprint.

\item ``Object-Centric Multi-View Aggregation'', S.Tulsiani, \underline{O.Litany}, CR.Qi, H.Wang, L.Guibas, Preprint.

\item ``FPGA system for real-time computational extended depth of field imaging using phase aperture coding'', T.Remez, \underline{O.Litany}, S.Yoseff, H.Haim, A.Bronstein, Preprint.

\end{enumerate}
