\begin{enumerate}
    \item Jan 21, 2026. Bosch Research.
    \item Dec 30, 2025. Amazon Research.
    \item Nov 23, 2025. Bar Ilan University's Learning Club Seminar. 
    \item August 4, 2025. Stanford University. Invited by Prof. Leonidas Guibas.
    \item April 23, 2025. Tel-Aviv University. Invited by Prof. Ishay Mansour.
    \item Nov 28, 2024. Weizmann  Computer Vision and AI seminar.
    \item Sep 29, 2024. Keynote at Sun3D workshop at ECCV. 
    \item May 30, 2024. Bar Ilan University CS Colloquium. Invited by Prof. Ely Porat.
    \item May 28, 2024. New-tech exhibition: AI, MACHINE LEARNING \& MACHINE VISION track.
    \item April 10, 2024. TUM, Germany. Invited by Prof. Daniel Cremers. 
    \item March 28, 2024. University of Illinois, Urbana-Champaign -- vision seminar. Invited by Prof. Shenglong Wang.
    \item March 26, 2024. Tel-Aviv University EE Seminar. Invited by Prof. Hadar Elor
    \item 3.15.24 ETH, Switzerland. Invited by Prof. Konrad Schindler. 
    \item IMVC Autonomous Systems \& Robotic Vision
    \item ICCV 2023 Workshop on Language for 3D Scenes - \href{https://languagefor3dscenes.github.io/ICCV2023/#:~:text=shapes%20(3DHighlighter).-,Or%20Litany,-He%20is%20a}{Keynote}. 
    \item 5.24.23 Singapore Vision Day -- \href{https://www.comp.nus.edu.sg/~leegh/svd/#:~:text=Keynote%20Talk%203%3A%20Data%20driven%20simulation%20for%20AV%20(Or%20Litany%3B%20Nvidia%2C%20Incoming%20Technion)}{Keynote}.
    \item 4.28.23 Brown Visual Computing Seminar
    \item Data-driven Simulation for AV, ECCV 2022 workshop on 3D Perception for Autonomous Driving. Tel-Aviv, Israel. Invited by Prof. Gal Chechik and Raja Giryes.
    \item 9.30.21 Research presentation at Nvidia's NTECH conference. 
    \item 9.29.21 Reduced supervision for 3D scene understanding. SIAM Conference on Geometric and Physical Modeling (GD/SPM21). Invited by Prof. Qixing Huang.
    \item 6.2.21 Deep Learning on graphs and manifolds. Guest speaker at Stanford course CS233.
    \item Nvidia GTC 2021
    \item 12.14.20 Hebrew University of Jerusalem (HUJI). Invited by Prof. Raanan Fattal. 
    \item 12.8.20 Tel-Aviv CS. Invited by Prof. Sivan Toledo.
    \item 12.1.20 Technion Pixel-Club. Invited by Prof. Ron Kimmel. 
    \item 11.30.20 Tel-Aviv EE. Invited by Prof. Shai Avidan.
    \item 10.16.20 UT Austin's Forum for Artificial Intelligence (FAI) seminar. Invited by Prof. Qixing Huang. 
    \item 9.9.20 Google Cambridge. Invited by Prof. Bill Freeman.
    \item 8.2.20 Talk at iGDL
    \item 7.29.20 Talk at Google. Invited by Prof. Thomas Funkhouser.
    \item 7.8.20 SIAM 20: Learning and Processing of Geometric Visual Structures. Invited by Prof. Ron Kimmel.
    \item 1.7.20 Talk at Amazon. Invited by Dr. Roee Litman.
    \item 9.1.20. Stanford Graphics-Cafe.
    \item 19.12.19. Talk at Nvidia Research, Toronto. Invited by Prof. Sanja Fidler
    \item 21.11.19. Talk at Apple. Invited by Dr. Oncel Tunzel
    \item 19.7.19. Invited speaker at the, ``Deep Learning for Science School'' at Berkeley.
    \item 17.4.2019. Cornell Tech University. Invited by Prof. Noah Snavely.
    \item 16.4.2019. New York University (NYU). Invited by Prof. Daniele Panozzo and Prof. Juan Bruna.
    \item 10.4.2019. Palo Alto Research Center (Xerox PARC). Invited by Kalai Ramea.
    \item 31.1.2019. ``San Francisco Deep Learning Meetup'', San Francisco, CA, USA.
    \item 4.7.2018. ``TUM IAS Workshop on Machine Learning for 3D Understanding'', TU Munich, Germany.
	\item 15.3.2018. ``Imaging and Vision from Theory to Applications'' workshop, Siegen, Germany. Invited by Prof. Michael Muller.
	\item 26.1.2018. Stanford University. Invited by Prof. Leonidas Guibas.
	\item 27.09.2017. New York University (NYU). Invited by Prof. Juan Bruna. 
	\item 13.09.2017. Google New York.  
	\item 26.06.2017. Invited speaker at Israel computer vision MeetUp. Google campus Tel-Aviv.	
	\item 13.01.2017. Invited speaker at the Dagstuhl Seminar 17021 “Functoriality in Geometric Data”. Schloss Dagstuhl, Leibniz Center for Informatics (Germany).	
	\item 25.12.2016. Invited speaker at the Israeli Computer Vision Day. IDC Herzliya (Israel).
	\item 24.11.2016. Weizmann Insitute of Science (Israel). Invited by Prof. Y. Lipman.
	\item 22.11.2016. Tel Aviv University (Israel). Invited by Prof. D. Cohen-Or.	
	\item 27.10.2016. Invited speaker at the G-Caffe Seminar, Stanford University. Invited by Prof. L. Guibas. 
	\item 21.06.2016. Eurographics Symposium on Geometry Processing (SGP), FU Berlin (Germany). Invited by Prof. M. Ovsjanikov and Prof. D. Panozzo.	
	\item 5.6.2016. The Hebrew University of Jerusalem (Israel). Invited by Prof. Shmuel Peleg.	
	\item 15.4.2016. Technische Universität München (Germany). Invited by Prof. D. Cremers.
	\item 12.4.2016. USI University of Lugano (Switzerland). Invited by Prof. M. Brsontein.		
	\item 30.11.2015. Ben Gurion University (Israel). Invited by Prof. O. Ben-Shahar.		
	
\end{enumerate}