\begin{itemize}
\item ``\href{https://opensun3d.github.io/index.html}{Open-Vocabulary 3D Scene Understanding}'' 6th workshop at CVPR, 2026.
\item ``\href{https://opensun3d.github.io/index.html}{Open-Vocabulary 3D Scene Understanding}'' 5th workshop at ICCV, 2025.
\item ``\href{https://opensun3d.github.io/index.html}{Open-Vocabulary 3D Scene Understanding}'' 4th workshop at CVPR, 2025.
\item ``\href{https://neural-fields-beyond-cams.github.io/}{Neural Fields Beyond Conventional Cameras}'' 2nd workshop at CVPR, 2025.
\item ``\href{https://neural-bcc.github.io/2024/2024.html}{Neural Fields Beyond Conventional Cameras}'' workshop at ECCV, 2024.
\item ``\href{https://opensun3d.github.io/index_eccv24.html}{Open-Vocabulary 3D Scene Understanding}'' 3rd workshop at ECCV, 2024.
\item ``\href{https://opensun3d.github.io/index_cvpr24.html}{Open-Vocabulary 3D Scene Understanding}'' 2nd workshop at CVPR, 2024.
\item ``\href{https://agents4ad.github.io/}{Data-Driven Autonomous Driving Simulation}'' workshop at CVPR, 2024.
\item ``\href{https://opensun3d.github.io/}{Neural Fields for Visual Computing}'' workshop at CVPR, 2024.
\item ``\href{https://neuralfields.cs.brown.edu/siggraph23.html}{Neural Fields for Visual Computing}'' Course at SIGGRAPH, 2023.
\item ``\href{https://opensun3d.github.io/index_iccv23.html}{3DOVScene: Open-Vocabulary 3D Scene Understanding}'' workshop at ICCV, 2023.
\item ``\href{https://neuralfields.cs.brown.edu/cvpr22.html}{Neural Fields in Computer Vision}'' workshop at CVPR, 2022.
\item ``\href{https://ivl.cs.brown.edu/3DReps/}{Learning 3D Representations for Shape and Appearance}'' workshop at ICCV, 2021.
\item ``\href{https://gdl-israel.github.io/iGDL2020.html}{iGDL: Israeli Geometric Deep Learning workshop (First)}'' workshop, 2020.
\item ``\href{https://gdl-israel.github.io/}{iGDL: Israeli Geometric Deep Learning workshop (Second)}'' workshop, 2021.
\item ``\href{https://geometry.stanford.edu/3DReps/index.html}{Learning 3D Representations for Shape and Appearance}'' workshop at ECCV, 2020.
\item ``\href{https://diglib.eg.org/handle/10.2312/egt20191036}{Deep Learning for Computer Graphics and Geometry Processing}'' tutorial at Eurographics, 2019.
\item ``\href{https://sites.google.com/view/eccv2018fmapstutorial/home}{Deep Learning meets Geometry}'' tutorial at ECCV, 2018.
\item ``\href{https://sites.google.com/view/dlgeometry/home}{Deep Learning and Geometry}'' workshop at EUSIPCO, 2017.
\end{itemize}