\documentclass[margin,line]{res}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}
\usepackage{color}
\usepackage{hyperref}
\usepackage{enumitem}

\begin{document}

\name{Or Litany \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2.5in}p{4in}}
Assistant Professor, Technion &  {\it E-mail:}  orlitany at gmail dot com \\
 and Senior Research Scientist, NVIDIA. &  {\it Homepage:} \url{https://orlitany.github.io} \\ 
 &  {\it Google Scholar:} \href{https://scholar.google.co.il/citations?user=Ihs8dwsAAAAJ&hl=en}{link}\\
\end{tabular}


\section{\sc Research Interests}
AI for Generative and Perception tasks in 3D Computer Vision and Graphics.

\section{\sc Education}
{\bf Tel Aviv University}, Tel Aviv, Israel\\
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D., Electrical Engineering, October 2018
\item[] Advisor:  Prof. Alex M. Bronstein
\end{list1}


{\bf Tel Aviv University}, Tel Aviv, Israel\\
\vspace*{-.1in}
\begin{list1}
\item[] M.Sc., Electrical Engineering, August 2012
\end{list1}

{\bf Hebrew University}, Jerusalem, Israel\\
%{\em Department of Mathematics and Statistics}
\vspace*{-.1in}
\begin{list1}
\item[] B.Sc., Physics and Mathematics,  August 2005
% \item[] Talpiot Program\footnote{An elite Israel Defense Forces training program, for recruits who have demonstrated outstanding academic ability in the sciences and leadership potential (Acceptance rate $< 0.5\%$).}: B.Sc., Physics and Mathematics,  August 2005\\

\end{list1}

\section{\sc Research \\ Experience}

{\bf Technion –- Israel Institute of Technology} 

\vspace{-.3cm}
{Assistant Professor}
\hfill {\bf September 2023 - Present}

{\bf NVIDIA}

\vspace{-.3cm}
{Sr. Research Scientist} \hfill {\bf August 2020 - Present}

\vspace{-.3cm}
{Manager: Prof. Sanja Fidler}

{\bf Stanford University}, CA, USA

\vspace{-.3cm}
{Postdoctoral Researcher} \hfill {\bf September 2019 - August 2020}

\vspace{-.3cm}
{Advisor: Prof. Leonidas Guibas}


{\bf Facebook AI Research}, CA, USA

\vspace{-.3cm}
{Postdoctoral Researcher} \hfill {\bf September 2018 - September 2019}

\vspace{-.3cm}
{Hosts: Prof. Leonidas Guibas and Prof. Jitendra Malik}

{\bf Technion}, Haifa, Israel 

\vspace{-.3cm}
{Postdoctoral Researcher} \hfill {\bf April 2018 - August 2018}

\vspace{-.3cm}
{Advisor: Prof. Alex Bronstein}

{\bf Google TLV} 

\vspace{-.3cm}
{Research Intern} \hfill {\bf December 2017 - August 2018}

\vspace{-.3cm}
{Transfer learning algorithms in Deep Learning; Host: Dr. Daniel Freedman}

{\bf Google NYC} 

\vspace{-.3cm}
{Research Intern} \hfill {\bf July 2017 - October 2017}

\vspace{-.3cm}
{Geometric deep-learning for shape completion}

{\bf Intel Perceptual Computing} 

\vspace{-.3cm}
{Research Intern} \hfill {\bf July 2016 - June 2017}

\vspace{-.3cm}
{3D shape correspondence}

{\bf Microsoft Research} 

\vspace{-.3cm}
{Research Intern} \hfill {\bf February 2015 - December 2016}

\vspace{-.3cm}
{3D scene understanding and reconstruction for VR}

{\bf Technische Universit\"{a}t M\"{u}nchen}, Munich, Germany 

\vspace{-.3cm}
{Visiting Scholar} \hfill {\bf March - May 2016,}

\vspace{-.3cm}
{Working on 3D shape analysis; Host: Prof. Daniel Cremers}
\hfill {\bf and April 2017}

{\bf Duke University}, North Carolina, USA

\vspace{-.3cm}
{Visiting Scholar} \hfill {\bf November 2014}

\vspace{-.3cm}
{Working on Computational Photography; Host: Prof. Guillermo Sapiro} 

\section{\sc Honors and Awards}
ICCV Outstanding reviewer, 2023
\vspace*{-2.5mm}

ICML Outstanding Paper Award (2 of 4,990 submissions), 2020
\vspace*{-2.5mm}

ICCV Best Paper Nomination (11 of 4,300 submissions), 2019
\vspace*{-2.5mm}

ICLR LLD workshop Best Paper Award, 2019

\vspace*{-2.5mm}
Elsevier Outstanding Reviewer, 2017

\vspace*{-2.5mm}
SGP Best Paper Award, 2016

%\vspace*{-2.5mm}
%Microsoft Research PhD Summer School travel grant, 2016

%\vspace*{-2.5mm}
%Runner-up for ADAMS Academy Fellowship, 2016

\vspace*{-2.5mm}
Microsoft Research top talent intern, 2016 

\vspace*{-2.5mm}
Weinstein prize for graduate studies, 2015

% \vspace*{-2.5mm}
% Google conference travel grant for ECCV, 2014

\vspace*{-2.5mm}
Tel Aviv University: graduated Magna Cum Laude, 2012


\section{\sc Fellowships and Grants}

AI for Science Moonshot grant, 2026
\vspace*{-2.5mm} %$10M split between 12 PIs

Israel Science Foundation (ISF) Personal Research Grant, 2025
\vspace*{-2.5mm} %$262K, 2025-2029

Israel Science Foundation (ISF) New-Faculty Equipment Grant, 2025
\vspace*{-2.5mm} %$327K, 2023-2028

Jacobs Technion-Cornell Institute Faculty Exchange Travel Grant, 2025 %7K USD
\vspace*{-2.5mm}

Meta academic gift, 2023
\vspace*{-2.5mm}

\href{https://www.google.com}{Azrieli Early Career Faculty Fellowship}, 2023 

\vspace*{-2.5mm}
Taub Fellowship, 2023

\vspace*{-2.5mm}
\href{https://misti.mit.edu/mit-israel-past-seed-fund-winners#:~:text=Or%20Litany%2C%20Technion%20%2D%20Israel%20Institute%20of%20Technology}{MISTI MIT Israel Zuckerman STEM Fund}, 2023

\vspace*{-2.5mm}
German Academic Exchange Service (DAAD) research grant, 2016

\vspace*{-2.5mm}
Google travel grant, 2014

\vspace*{-2.5mm}
\href{https://ellis.eu/}{European Laboratory for Learning and Intelligent Systems (ELLIS)} Scholar

\section{\sc Publications}
\input{publications}

\input{advising}

\section{\sc Selected Professional Service}

\begin{list2}
\item Program Chair (PC) for 3DV 2027
\item Doctoral Consortium Chair at ECCV 2024-2026. 
\item Research Interaction Chair at 3DV 2024-2025.
\item Area Chair: ECCV 2024-2026, CVPR 2025-2026, ICCV 2025, 3DV 2022-2026.
\item Workshop / tutorial organizer:
\input{workshops}
\item Mentor at the Doctoral Consortium: CVPR 2020, CVPR 2022, ICCV 2023. 
\item Reviewer at: \\
Grants: SNSF, ISF; \textbf{2016}: ECCV; \textbf{2017}: 3DV, CVPR; \textbf{2018}: CVPR, TPAMI, Pattern Recognition, ICASSP, ECCV, 3DV, Transactions on Graphics (TOG), NIPS, SIGGRAPH ASIA, GMDL workshop; \textbf{2019}:  Eurographics, CVPR, IEEE Robotics and Automation Letters, Computer Vision for Global Challenges Workshop at CVPR, GMDL workshop at ICCV, 3DRW workshop at ICCV, TPAMI, Transactions on Image Processing, AAAI, ICLR (emergency); \textbf{2020}: CVPR, Siggraph, NeurIPS, CAG journal (Elsevier), Journal of Imaging, 3DOR, IEEE TVCG, PAMI. \textbf{2021}: CVPR, WACV, ICCV, NeurIPS, TPAMI, IEEE  Robotics  and  Automation  Letters. \textbf{2022}: SIGGRAPH, CVPR, TMLR, 3DV, NeurIPS. \textbf{2023}: CVPR, WAD workshop, SIGGRAPH, ICCV, OpenSUN3D workshop. \textbf{2024}: ICLR, CVPR, NeurIPS, SIGGRAPH. \textbf{2025}: NeurIPS, ICLR, ICML, SIGGRAPH-ASIA \textbf{2026}: ICLR, ICML. 
\item Thesis Examiner: Harel Yedid, MSc (Technion), Ron Rephaeli, MSc (Technion); Liav Hen, MSc (TAU); Etai Sella, MSc (TAU); Yarin Bar, MSc (Technion); Yanai Soker, MSc (Technion); Shengyu Huang, PhD (ETH Zurich);  Marco Fumero, PhD (University of Rome); Maxim Maximov, PhD (TUM), Evin Pınar Ornek, PhD (TUM); Edan Kinderman, MSc (Technion); Saar Tsour, MSc (Technion); Itay Segev, MSc (Technion); 
\end{list2}

\section{\sc Invited Talks}
\input{talks}

\end{resume}
\end{document}